### 2019-08-01 paper/conclusion.tex
AVR argument

We found that groups of K dwarfs, selected to be coeval using the
\citet{angus2019} gyrochronology relation, do {\it not} have the same velocity
dispersion across all temperatures.
This indicates that {\it either} the \citep{angus2019} period-color relation
is wrong, {\it or} that mass-dependent dynamical heating is affecting this
data set.
We presented three pieces of evidence that suggest mass-dependent heating
cannot be responsible for all of the increasing velocity dispersion.

@@

\item{No strong evidence for mass-dependent heating has been found among M, L
and T-type stars.
These low-mass stars live longer than the current age of the Universe and
therefore do not suffer from a mass-age degeneracy \citep{faherty2009}.}

\item{Literature measurements of the (\vz) AVR exponent are slightly higher
than the value measured from our data set, but calculated using more massive
stars.
Mass-dependent dynamical heating should however produce a {\it smaller} AVR
exponent for higher-mass stars.
We acknowledge that the stars in the \mct\ sample, analyzed in this work, are
subject to different selection biases than those used to calculate AVRs in the
literature \citep{holmberg2009, aumer2009, yu2018}, so drawing direct
comparisons between them is not a robust test.}

\item{The differences in the (\vb) AVR exponent between the hottest and
coolest K dwarfs in our sample are extremely large, spanning values between
0.3 and 0.65, yet the difference in mass is less than a factor of two.
Such a large spread in AVR exponents cannot be explained by mass-dependent
heating alone.}

>>>>

We found that old groups of K dwarfs selected to be coeval using the
\citet{angus2019} gyrochronology relation do {\it not} have the same velocity
dispersion across all temperatures.
This indicates that either the \citep{angus2019} period-color relation is
wrong, or that mass-dependent dynamical heating is affecting this data set.
We presented three pieces of evidence that suggest mass-dependent heating
cannot be responsible for all of the increasing velocity dispersion.

@@

\item{
        No strong evidence for mass-dependent heating has been found among M, L
and T-type stars.
These low-mass stars live longer than the current age of the Universe and
        therefore do not suffer from a mass-age degeneracy
        \citep{faherty2009}.
}

\item{
        Literature measurements of the (\vz) AVR exponent are slightly higher
than the value measured from our data set, but calculated using more massive
stars.
Mass-dependent dynamical heating should however produce a {\it smaller} AVR
        exponent for higher-mass stars.
We acknowledge that the stars in the \mct\ sample, analyzed in this work, are
        subject to different selection biases than those used to calculate
        AVRs in the literature \citep{holmberg2009, aumer2009, yu2018}, so
        drawing direct comparisons between them does not provide a reliable
        test.
}

\item{
        The differences in the (\vb) AVR exponent between the hottest and
coolest K dwarfs in our sample are extremely large, spanning values between
0.4 and 0.75, yet the difference in mass is less than a factor of two.
Such a large spread in AVR exponents cannot be explained by mass-dependent
        heating alone.
}

### 2019-08-01 paper/results.tex
AVR argument

To investigate further, we calculated the exponent of the (\vb) AVR for each
temperature bin in figure \ref{fig:age_cut}.
\begin{figure}
  \caption{
The exponent of the AVR as a function of effective temperature.
    The AVR exponent of \citet{holmberg2009}, calculated using a more massive
    sample of stars, is shown as a horizontal dashed line.
}
  \centering
    \includegraphics[width=1\textwidth]{AVR_exponent}
\label{fig:AVR_exponent}
\end{figure}

>>>>

To investigate further, we calculated the exponent of the (\vb) AVR for each
temperature bin in figure \ref{fig:age_cut}.
\begin{figure}
  \caption{
      The exponent of the (\vb) AVR as a function of effective temperature.
}
  \centering
    \includegraphics[width=1\textwidth]{AVR_exponent}
\label{fig:AVR_exponent}
\end{figure}
Figure \ref{fig:AVR_exponent} shows the significant rise the in AVR exponent
as a function of effective temperature.
The hottest stars in our sample (\teff\ = 4833-5000 K) have a (\vb) AVR
exponent of 0.39 $\pm$ 0.02 and the coolest (\teff\ = 3500-3667 K) have an
exponent of 0.74 $\pm$ 0.02.
The masses of stars in our sample differ by less than a factor of two,
so mass-dependent heating cannot be entirely responsible for this large spread
in heating rates.
\racomment{Need to look into this further.}
